---
title: "RNA Analysis"
output: html_document
date: "2026-06-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction

### Abstract

### Objectives

### Methods

### Results

## R Code

### Libraries
```{r libraries, message = FALSE}
  library("tidyverse")
  library("ComplexHeatmap")
  library("circlize")
  library("ClassComparison")
  library("effectsize")
  library("magrittr")
```
### Data Loading and Processing
```{r data}
  setwd("C:/Users/Lyhuang/Downloads/Data")

  sample_data <- 
    read.csv("Samples.csv") %>% 
    mutate(Sample = str_replace_all(Sample,"-",".")) %>% 
    as_tibble()
  
   pool_data <- 
      read.csv("pool.tpm_Gene.csv") %>%  
      column_to_rownames(var = "X") %>% 
      mutate(across(where(is.double), ~add(.x, 1))) %>% 
      mutate(across(where(is.double), log2)) %>% 
      t() %>% 
      as.data.frame() %>% 
      rownames_to_column(var = "Sample")
   
    a_data <- pool_data %>% 
      semi_join(sample_data %>% 
      filter(TimePoint == "48H"), by = join_by(Sample)) %>% 
      column_to_rownames(var = "Sample") %>% 
      t()
    
    a_classes <- 
      sample_data %>% 
      filter(TimePoint == "48H") %>% 
      select(Group) %>% pull(Group) %>% 
      factor()
    
    b_data <- 
      pool_data %>% 
      semi_join(sample_data %>% 
      filter(TimePoint == "72H"), by = join_by(Sample)) %>% 
      column_to_rownames(var = "Sample") %>% 
      t()
    
    b_classes <- 
      sample_data %>% 
      filter(TimePoint == "72H") %>% 
      select(Group) %>% pull(Group)%>% 
      factor()
    
    c_data <- 
      pool_data %>% 
      semi_join(sample_data %>% 
      filter(Treatment == "TTFields"), by = join_by(Sample)) %>% 
      column_to_rownames(var = "Sample") %>% 
      t()
    
    c_classes <- 
      sample_data %>% 
      filter(Treatment == "TTFields") %>% 
      select(Group) %>% pull(Group)%>% 
      factor()
    
    Pvalcut<-c(0.00001,0.0001,0.001,0.005,0.01,0.05,seq(0.1,1,by=0.05))
```
First the working directory is set. Then, the data is loaded in from 2 sources: sample data from Samples.csv and genetic data from pool.tpm_gene.csv.The genetic data has the function log_2(x + 1) applied and the data is arranged for ease of legibility for the proceeding data analysis.

### Data Analysis
```{r}
  a_mttest <- MultiTtest(a_data, a_classes, na.rm = FALSE)
  a_bum <- Bum(a_mttest@p.values)
  hist(a_bum, main = "48H")
  a_significant_genes <- a_data[selectSignificant(a_bum, alpha = .05, by = "FDR"),] %>% na.omit()
```
Using MultTtest, multiple t-tests are run to produce p-values for the significance of every gene. These p-values are then evaluated using the Bum (Beta-Uniform Mixture) class to analyze p-value distribution The beta-uniform mixture graph shows a strong spike near 0, following a beta distribution as opposed to a uniform distribution, denoting the presence of truly significant p-values. Significant genes are identified using the Benjamini-Hochberg method to control false discovery rates to .05.

```{r}  
  b_mttest <- MultiTtest(b_data, b_classes, na.rm = TRUE)
  b_bum <- Bum(b_mttest@p.values)
  hist(b_bum, main = "72H")
  b_significant_genes <- b_data[selectSignificant(b_bum, alpha = .05,by = "FDR"),] %>% na.omit()
  
  c_mttest <- MultiTtest(c_data, c_classes, na.rm = FALSE)
  c_bum <- Bum(c_mttest@p.values)
  hist(c_bum, main = "TTFields")
  c_significant_genes <- c_data[selectSignificant(c_bum, alpha = .05,by = "FDR"),] %>% na.omit()
```
This is then repeated to compare
### Graphs

### Acknowledgements and Citations







